---
title: Diamonds
author: Jun Cheng Guo
date: '2020-04-03'
categories:
  - Daily Blog
tags:
  - markdown
  - R Studio
  - Projects
slug: Diamonds
images:
  - img/2020/01/Diamond.jpg
type: post
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
***

## Dataset: diamonds 

This data contains the prices and other attributes of almost 54,000 diamonds.

```{r message=FALSE, include=FALSE}
library(tidyverse)
library(gridExtra)
str(diamonds)
?diamonds
```

### Scatterplot

  - `price` as the $y$-axis and `carat` as the $x$-axis.
  
- **Quality of Cut as Color, Adjusted for Transparency **

```{r echo=FALSE, fig.align='center'}
# add your graph here

ggplot(
  
  diamonds
  
  )+
  
  geom_point(
  aes(
    
    x = carat,
    y = price,
    colour = cut
  ),
  
  alpha = 2/10
  
  )



```

- **As a diamond get bigger, its price increases. As a diamond's cut gets more luminous, its price increases. The bigger the diamond, the more effect its cut has on price**
  
### Boxplot


- **`carat` as the $y$-axis and `cut` as the $x$-axis** 

```{r echo=FALSE, fig.align='center'}
# add your graph here
bp<-ggplot(
  
  diamonds
  
)+
  
  geom_boxplot(
    
    aes(
      
      x = cut,
      y = carat 
      
    ),
    
    fill = rgb(2/255, 105/255, 164/255)
    #Medium Persian Blue
  )
bp + coord_flip()
```

- **On average, Fair Diamonds are larger than Ideal diamonds. The largest Fair Diamond is 5 carats while the largest Ideal diamond is 3.5 carats**


### Histogram


- **Diamond Distribution** 
  

```{r echo=FALSE, fig.align='center'}
# add your graph here
ggplot(
  
  diamonds
  
  )+
  
  geom_histogram(
    
    aes(
      
      x = carat,
      
    ),
    
    bins = 50,
    fill = rgb(254/255, 124/255, 0/255), #Amber
    color = rgb(2/255, 105/255, 164/255) #Medium Persian Blue
    
  )
```
- **There are many small diamonds, but few larger than 3 carats**
